---
title: "leaflet"
author: "Victoria"
date: "11 de mayo de 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Leaflet 1.1

The first thing is to install leaflet package. The leaflet package allow us to create a map widget that we can store in a variable so that we can modify the map later on. 

install.package(leaflet)

Once we have the package installed we have to call it. In this first graph we are going to create a world map. Leaflet can be used with html output. 

```{r }
library(leaflet)
my_map<-leaflet()%>%
        addTiles()
my_map
``` 

This code is the same that: 

```{r, eval=FALSE }

my_map<-leaflet()
my_map<-addTiles(my_map)
my_map
```
If we want to add a Marker we need the latitud and longitud information. 

```{r,  }
my_map<-my_map%>%addMarkers(lat=-34.9035643, lng=-56.2003770, popup="Vicky y magui en el BCU")
my_map
```
```{r }
library(leaflet)
my_map<-leaflet()%>%
        addTiles()
my_map
``` 

That is the same that: 

```{r , eval=FALSE}
my_map<-addMarkers(my_map, lat=-34.9035643, lng=-56.2003770, popup="Vicky y magui en el BCU")
my_map
``` 

## Add multiple markers

To add multiple markers you need to have a data frame with latitute and long.

```{r, message=FALSE, warning=FALSE}
set.seed(2016-04-25)
df<-data.frame(lat=runif(20, min=39.2, max=39.3),lng=runif(20, min=-76.6, max=-76.5))

df%>%
leaflet()%>%
addTiles()%>%
addMarkers() 

``` 
### Custom Markers 
```{r, message=FALSE, warning=FALSE}
hopkinsIcon<-makeIcon(iconUrl="http://brand.jhu.edu/content/uploads/2014/06/athletics.png", iconWidth=31*215/230, iconHeight=31)

hopkinsLatLong<-data.frame(
        lat=c(39.2973166, 39.3288851, 39.2906618, 39.2970681,39.2824806), lng=c(-76.5929798,-76.6206598,-76.5469683,-76.6150537,-76.6016766)
)

hopkinsLatLong%>%
leaflet()%>%
addTiles()%>%
addMarkers(icon=hopkinsIcon) 

``` 

To add links in the icons 
```{r, message=FALSE, warning=FALSE}

hopkinsSite<-c( 
"<a href=' http://www.jhsph.edu/'> East Baltimore Campus</a>",
 "<a href=' http://apply.jhu.edu/visit/homewood/'> Homewood Campus</a>",
 "<a href=' http://www.hopkinsmedicine.org'> Medical Center</a>",
 "<a href=' http://www.peabody.jhu.edu'> Peabody institute </a>",
 "<a href=' http://www.carey.jhu.edu'> Carey Nusiness School </a>")

hopkinsLatLong%>%
        leaflet()%>%
        addTiles()%>%
        addMarkers(icon=hopkinsIcon, popup=hopkinsSite)
```
## Present the Markers in cluster

```{r, message=FALSE, warning=FALSE}
df<- data.frame(lat=runif(20, min=39.25, max=39.35), lng=runif(20, min= -76.65, max=-76.55))

df%>%
leaflet()%>%
addTiles()%>%
addMarkers(clusterOptions=markerClusterOptions())

```

Instead of adding cluster we can add circle markers using 'addCircleMarkers()'

```{r, message=FALSE, warning=FALSE}
df<- data.frame(lat=runif(20, min=39.25, max=39.35), lng=runif(20, min= -76.65, max=-76.55))

df%>%
leaflet()%>%
addTiles()%>%
addCircleMarkers()

```
You can draw arbitrary shapes on the maps you create, including circles and squares. The code below draws a map where the circle on each city is proportional to the population of that city.

```{r, message=FALSE, warning=FALSE}
md_cities <- data.frame(name = c("Baltimore", "Frederick", "Rockville", "Gaithersburg", 
                                 "Bowie", "Hagerstown", "Annapolis", "College Park", "Salisbury", "Laurel"),
                        pop = c(619493, 66169, 62334, 61045, 55232,
                                39890, 38880, 30587, 30484, 25346),
                        lat = c(39.2920592, 39.4143921, 39.0840, 39.1434, 39.0068, 39.6418, 38.9784, 38.9897, 38.3607, 39.0993),
                        lng = c(-76.6077852, -77.4204875, -77.1528, -77.2014, -76.7791, -77.7200, -76.4922, -76.9378, -75.5994, -76.8483))
md_cities %>%
  leaflet() %>%
  addTiles() %>%
  addCircles(weight = 1, radius = sqrt(md_cities$pop) * 30)

```
```{r, message=FALSE, warning=FALSE}

leaflet() %>%
  addTiles() %>%
  addRectangles(lat1 = 37.3858, lng1 = -122.0595, 
                lat2 = 37.3890, lng2 = -122.0625)

```

## Adding Legends
Adding a legend can be useful if you have markers on your map with different colors:
```{r, message=FALSE, warning=FALSE}
df <- data.frame(lat = runif(20, min = 39.25, max = 39.35),
                 lng = runif(20, min = -76.65, max = -76.55),
                 col = sample(c("red", "blue", "green"), 20, replace = TRUE),
                 stringsAsFactors = FALSE)

df %>%
  leaflet() %>%
  addTiles() %>%
  addCircleMarkers(color = df$col) %>%
  addLegend(labels = LETTERS[1:3], colors = c("blue", "red", "green"))


```

